\sect{Questions Concerning the Lecture}

\qv{In your estimate, which percentage of the students remains in comparison to the start of term?}{0--20\%}{20--40\%}{40--60\%}{60--80\%}{80--100\%}{v5}

\qiv{Does your knowledge match the previous knowledge expected by the lecturer?}{fully}{}{}{not at all}{v6}

\qv{Have the learning targets been clearly defined?}{fully}{}{}{}{not at all}{v7}

\qiii{What do you think of the range of contents?}{too broad}{appropriate}{too small}{v8}

\qv{Are the awarded credit points adequate in view of your amount of work (1\,CP corresponds to 25-30\,h)?}{way to few}{}{just right}{}{way to many}{v9}

\qv{How do you estimate your learning gain?}{very high}{}{}{}{very low}{v10}

\qv{In your estimation, what is the pace of the lecture?}{way too fast}{}{just right}{}{way too slow}{v11}

\qv{How do you rate the structure of the course?}{perfect}{}{}{}{none}{v12}

\qv{How comprehensible is the curriculum conveyed?}{very well}{}{}{}{very badly}{v13}

\qiv{What do you think of the lecturer's style?}{motivating}{}{}{frustrating}{v14}

\qiv{Does the level of detail correspond to the importance?}{\small{perfectly}}{}{}{not at all}{v15}

\qiv{How well does the lecturer explain difficult subjects?}{very well}{}{}{very badly}{v16}

\qii{Does the lecturer manage to stress important subjects?}{yes}{no}{v17}

\qii{Is the choice of presentation (blackboard/slides/\dots) appropriate?}{yes}{no}{v18}

\qiv{How well is the presentation done? (legibility of blackboard writing/\dots)}{very good}{}{}{really bad}{v19}

\qivm{Are there any problems concerning the presentation? If so, what are they?}{none}{queer way of presentation}{writing not legibly}{other}{v20}

\qiv{How are the lecturer's verbal skills?}{very well}{}{}{very badly}{v21}

\qvm{Are there any problems concerning the language or acoustic understanding?}{none}{too quiet/ technical problems}{lack of knowledge of language}{students too noisy}{other}{v22}
\normalsize

\np

\sect{Questions Concerning the Lecture}

\qii{During (or after) the lecture are you nervous about asking questions?}{yes}{no}{v23}

\qv{Does the lecturer respond to students' needs and questions?}{yes}{}{}{}{no}{v24}

\qiv{How does the lecturer answer questions?}{very well}{}{}{very badly}{v25}

\qv{How useful is the material provided for the lecture? (script/slides/\dots)}{very}{}{}{useless}{non-existing}{v26}

\qvi{Please give an overall mark for the lecture: \hspace{5cm}\small{(1 = very good, 6 = insufficient)}}{1}{2}{3}{4}{5}{6}{v27}

\qii{Would you recommend this lecture with this lecturer?}{yes}{no}{v28}

\kommentar{Do you have comments regarding the lecture? If so, please give keywords:}{vComment}{-vorlcomment}{2972997}

\sect{Questions concerning the study groups}

\qiii{Do you attend your study group?}{yes}{sometimes}{no}{u1}

\qvm{Are there problems regarding the organization of the study groups? If so, what are they?}{none}{too few\quad groups}{organization\- of enlisting}{schedule problems}{other}{u2}

\qiv{How well do the exercises match the lecture?}{very well}{}{}{very badly}{u3}

\qiv{Are the problems posed well? (no mistakes/clear instructions)}{yes}{}{}{not at all}{u4}

\qiii{How high is the standard of the questions? How difficult are they?}{too high}{perfect}{too low}{u5}

\qv{How much time do you need to complete the exercises?}{<4 h}{4--6 h}{6--8 h}{8--10 h}{> 10 h}{u6}

\qiv{Is your study group tutor a good teacher?}{yes}{}{}{not at all}{t1}

\qiv{Do you believe your study group tutor to be competent in the subject matter?}{yes}{}{}{not at all}{t2}

\qiv{How well is she/he prepared?}{very well}{}{}{not at all}{t3}

\qiv{Does she/he respond to questions concerning the lecture?}{very much}{}{}{not at all}{t4}

\qiiim{Does she/he use the time efficiently? If not, what would you improve?}{yes}{more about exercises}{more about lecture}{t5}

\qiv{Does your study group tutor motivate you?}{very much}{}{}{not at all}{t6}

\qiv{Does she/he explain things well?}{very well}{}{}{not at all}{t7}

\qiv{Do you understand her/him? (acoustics, language)}{very well}{}{}{badly}{t8}

\qiv{Does she/he correct your exercises thoroughly?}{very}{}{}{not at all}{t9}

\qiv{Do you find your study group useful?}{very useful}{}{}{useless}{t10}

%\stefanistdoof
\kommentar{Comments concerning the study group and your tutor:}{uComment}{-tutcomment}{3530434}

\rule{19cm}{1pt}

